Sumbission Steps

### 2021-01-06 code/01-raw-file-compression.Rmd
updated the code files based on new version of paper

---
title: "Compression of Raw Files"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

@@

```{r}
zip(
  zipfile = "../figure-static/figure-08-1.png.zip",
  files =  "../figure-static/figure-08-1.png"
)
```

>>>>

---
title: "Compression of Raw Files"
author: "Katherine Goode"
date: "<br>`r format(Sys.time(), '%B %d, %Y')`"
output: rmarkdown::github_document
---

@@

```{r}
zip(
  zipfile = "../figure-static/figure-06-1.png.zip",
  files =  "../figure-static/figure-06-1.png"
)
```

### 2021-01-06 code/03-submission-steps.Rmd
updated the code files based on new version of paper

    ```{r}
    # Individual files to delete
    file.remove("../data/bullet-explain.rds")
    file.remove("../data/bullet-lime.rds")
    file.remove("../data/bullet-rf.rds")
    file.remove("../data/bullet-test.csv")
    file.remove("../data/bullet-test.csv.zip")
    file.remove("../data/bullet-train.csv")
    file.remove("../data/bullet-train.csv.zip")
    file.remove("../data/example-signatures.csv")
    file.remove("../data/example-signatures.csv.zip")
    file.remove("../data/sine-lime-explain.rds")
    file.remove("../data/raw/h224-set1-features.rds")
    file.remove("../data/raw/h224-set1-features.rds.zip")
    file.remove("../data/raw/h224-set11-features.rds")
    file.remove("../data/raw/h224-set11-features.rds.zip")
    file.remove("../data/raw/CCFs_withlands.csv")
    file.remove("../data/raw/CCFs_withlands.csv.zip")
    file.remove("../data/raw/signatures.rds")
    file.remove("../data/raw/signatures.rds.zip")
    file.remove("../figure-static/figure-08-1.eps")
    file.remove("../figure-static/figure-08-1.png.zip")
    file.remove("../figure-static/figure-10-1.eps")
    file.remove("../figure-static/figure-10-1.png")

    # Folders to delete
    unlink("../figure", recursive = TRUE)
    unlink("../submission", recursive = TRUE)
    ```

@@

5. Run the following code to move all files necessary to the submission folder.

@@

    # Create a submission folder file path:
    submission_folder <- "../submission"

@@

    # Copy files to the submission folder
    file.copy("../paper.tex", submission_folder)
    file.copy("../paper.pdf", submission_folder)
    file.copy("../references.bib", submission_folder)
    file.copy("../WileyNJD-AMS.bst", submission_folder)
    file.copy("../WileyNJD-v2.cls", submission_folder)
    ```

6. Manually delete `figure/` and `figure-static/` from the figure file paths in `paper.tex`. For example, change `\includegraphics[width=6.5in]{figure/figure-01-1}` to `\includegraphics[width=6.5in]{figure-01-1}`.

7. Compile the file `paper.tex` to make sure it compiles correctly (especially references). (If using texShop, make sure to compile using LaTex, then bibTex, then LaTeX twice more.)

8. Besides for `paper.pdf`, delete all other files generated when `paper.tex` was compiled. This includes other paper files and pdf versions of the figures.

@@

9. Upload all remaining files in the submission folder to the ASA Data Science Journal submission page which should be:

  - `code-and-data.zip`
  - `figure-01-1.eps` through `figure-C3-1.eps`
  - `paper.pdf`
  - `paper.tex`
  - `references.bib`
  - `WileyNJD-AMS.bst`
  - `WileyNJD-v2.cls`

>>>>

    ```{r}
    # Specify date of submission folder
    submission_date = "2021-01-06"

    # Create a submission folder file path:
    submission_folder <- paste0("../submissions/", submission_date)

    # Individual files to delete
    file.remove("../data/bullet-explain.rds")
    file.remove("../data/bullet-explain-perms-clean.rds")
    file.remove("../data/bullet-lime.rds")
    file.remove("../data/bullet-rf.rds")
    file.remove("../data/bullet-test.csv")
    file.remove("../data/bullet-test.csv.zip")
    file.remove("../data/bullet-train.csv")
    file.remove("../data/bullet-train.csv.zip")
    file.remove("../data/example-signatures.csv")
    file.remove("../data/example-signatures.csv.zip")
    file.remove("../data/sine-data-test.rds")
    file.remove("../data/sine-data-train.rds")
    file.remove("../data/sine-lime-explain.rds")
    file.remove("../data/raw/h224-set1-features.rds")
    file.remove("../data/raw/h224-set1-features.rds.zip")
    file.remove("../data/raw/h224-set11-features.rds")
    file.remove("../data/raw/h224-set11-features.rds.zip")
    file.remove("../data/raw/CCFs_withlands.csv")
    file.remove("../data/raw/CCFs_withlands.csv.zip")
    file.remove("../data/raw/signatures.rds")
    file.remove("../data/raw/signatures.rds.zip")
    file.remove("../figure-static/figure-06-1.eps")
    file.remove("../figure-static/figure-06-1.png.zip")
    file.remove("../figure-static/figure-08-1.eps")
    file.remove("../figure-static/figure-08-1.png")

    # Folders to delete
    unlink("../figure", recursive = TRUE)
    unlink(submission_folder, recursive = TRUE)
    unlink("../support-info/figure", recursive = TRUE)
    ```

@@

5. Knit the supporting information document `support-info/supporting-information.Rnw`.

6. Run the following code to move all files necessary to the submission folder.

@@

@@

    # Copy files to the submission folder
    file.copy("../paper.tex", submission_folder)
    file.copy("../paper.pdf", submission_folder)
    file.copy("../references.bib", submission_folder)
    file.copy("../WileyNJD-AMS.bst", submission_folder)
    file.copy("../WileyNJD-v2.cls", submission_folder)

    # SUPPORTING INFORMATION

    # Copy the supporting information pdf to the submission folder
    file.copy("../support-info/supporting-information.pdf", submission_folder)
    ```

7. Manually delete `figure/` and `figure-static/` from the figure file paths in `paper.tex`. For example, change `\includegraphics[width=6.5in]{figure/figure-01-1}` to `\includegraphics[width=6.5in]{figure-01-1}`.

8. Compile the file `paper.tex` to make sure it compiles correctly (especially references). (If using texShop, make sure to compile using LaTex, then bibTex, then LaTeX twice more.)

9. Besides for `paper.pdf`, delete all other files generated when `paper.tex` was compiled. This includes other paper files and pdf versions of the figures.

@@

10. Upload all remaining files in the submission folder to the ASA Data Science Journal submission page which should be:

  - `code-and-data.zip`
  - `figure-01-1.eps` through `figure-B1-1.eps`
  - `paper.pdf`
  - `paper.tex`
  - `references.bib`
  - `supporting-information.pdf`
  - `WileyNJD-AMS.bst`
  - `WileyNJD-v2.cls`
